---
title: ""
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3


---

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE, eval=F)
```
<div class="row">
<div class="col-sm-6">
elephants' graveyard of frequently used code

## tidyverse

Using the faraway package in R: <a href = "https://cran.r-project.org/web/packages/faraway/faraway.pdf" target = "_blank"> Documentation </a> 

```{r}
#install.packages("faraway")
library(faraway)
data(seatpos)
head(seatpos)


```
### dplyr functions

filter, select, mutate, group by, summarise

```{r}
seatpos %>%
  filter(Age < 60 & Weight < 200) %>%
  select(Age, Weight) %>%
  mutate(decades = case_when(Age <=30 ~ "twenties",
                             Age <= 40 & Age >30 ~ "thirties",
                             Age <= 50 & Age >40 ~ "forties",
                             Age <= 60 & Age > 50 ~ "fifties")) %>%
  group_by(decades) %>%
  summarise(mean_Weight = mean(Weight))

         
```

### gather

gather columns into rows
```{r}
data("mtcars")
head(mtcars)
mtcars <- rownames_to_column(mtcars, "Model") %>%
  select(mpg, cyl, Model) %>%
  filter(cyl == 4)

gather(mtcars, "attribute", "this", 1:2)
```

### spread

spreads rows into columns

```{r}
data(mtcars)
mtcars <- rownames_to_column(mtcars, "Model") %>%
  select(mpg, cyl, Model)

spread(mtcars, key = 'cyl', value = 'mpg')

```

## linear modeling

linear models

### anova


```{r, eval=F}
### one way anova
library(faraway)
data(coagulation)
head(coagulation)

# boxplot
plot(coag ~ diet,coagulation,xlab="Diet",ylab="Coagulation Time")

# anova
anova(lm(coag ~ diet,coagulation))

# pairwise
tk_coag <- TukeyHSD(aov(coag ~ diet,coagulation))
tk_coag
plot(tk_coag)
```

### linear regression


``` {r}
# multiple regression
library(faraway)
data(savings)
head(savings)


## overall test
m1 <- lm(sr ~ pop15 + pop75 + dpi + ddpi,savings)
summary(m1)

# f stat for the overall test
ssy <- sum((savings$sr - mean(savings$sr))^2) # sum square y
sse <- deviance(m1) # residual sum of squares
df.residual(m1) # degress of freedom for the sse
fstat <- ((ssy-sse)/4)/(sse/df.residual(m1)) # F statistic for the overall test
1 - pf(fstat,4,df.residual(m1)) # p value

## partial f test

m2 <- lm(sr ~ pop75 + dpi + ddpi,savings) # reduced model
sse2 <- deviance(m2) # SSE for reduced model
fstat2 <- (deviance(m2)-deviance(m1))/(deviance(m1)/df.residual(m1))
1-pf(fstat2,1,df.residual(m1))


```
### interactions

``` {r}

library(faraway)
data(teengamb)

# income and sex on outcome
m1 <- lm(gamble ~ income + sex,teengamb)
#income, sex, and interaction between both
m2 <- lm(gamble ~ income + sex + income*sex,teengamb)

```

### correlation

``` {r}

library(faraway)
data(stat500)

m1 <- lm(final ~ midterm,stat500)
summary(m1)
sum(coef(m1)* c(1,83))
# confidence interval for beta 1
confint(m1)

# correlation

cor(stat500$final,stat500$midterm)

```
## functions and loops


### sample for loop
``` {r}
data(GSSvocab)
EGE<-rep(0,500)
for (i in 1:500)
{
  temp0<-na.omit(GSSvocab)
  index<-sample(1:27360,27360,replace=T) # random index
  temp1<-temp0[index,] # random sample of all data
  NewTrain<-temp1[1:13680,] # training data
  NewTest<-temp1[13681:27360,] # test data
  out<-lm(vocab~gender+nativeBorn+ageGroup+
             educGroup+age+educ,data=NewTrain)
  EGE[i]<-var(NewTest$vocab-predict.lm(out, newdata=NewTest))
}
summary(EGE)
hist(EGE,breaks = 20)
qqnorm(EGE)
quantile(EGE,probs=c(.025,.975))

```

### sample function
``` {r}
clean_live_frame_function <- function(livedata, albumname)  {
  artist_live_edits <- livedata %>%
    mutate(livemarker = ifelse(livedata$album_name == albumname, 1, 0))
  artist_live_edits2 <- artist_live_edits %>%
    mutate(omitvariable = case_when(
      (str_detect(album_name, "Sessions") |
         str_detect(album_name, "Live") |
         str_detect(album_name, "Festival") |
         str_detect(album_name, "Concerts"))& livemarker == 0 ~ "omit"))
 artist_live_edits2 <- artist_live_edits2 %>%
    mutate(omitvariable2 = case_when(
      (str_detect(track_name, "Live") & livemarker == 0 ~"omit")
    ))
 artist_live_edits2 <- artist_live_edits2 %>%
   filter(is.na(omitvariable) & is.na(omitvariable2))
 artist_live_edits2 <- artist_live_edits2 %>%
   distinct()
}

```

## python code

### pandas

``` {r setup2, include = FALSE}
#install.packages("reticulate")
library(reticulate)
use_python("/home/rstudio-user/.local/share/r-miniconda/envs/r-reticulate/bin/python")
knitr::knit_engines$set(python = reticulate::eng_python)

```


``` {python}
knitr::knit_engines$set(python = reticulate::eng_python)
import pandas as pd
import numpy as np
from sklearn import linear_model
from sklearn.model_selection import train_test_split

from sklearn.datasets import load_boston

boston = load_boston()
boston

```
