---
title: ''
output:
  html_document:
    toc: yes
    toc_float: yes
    collapsed: no
    number_sections: no
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '3'
---

---



```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE, eval=F)
```


<div class="row">
<div class="col-sm-6">
elephants' graveyard of frequently used (and forgotten) code

## tidyverse

Using the faraway package in R: <a href = "https://cran.r-project.org/web/packages/faraway/faraway.pdf" target = "_blank"> Documentation </a> 

```{r}
#install.packages("faraway")
library(tidyverse)
library(faraway)
data(seatpos)
head(seatpos)


```
### dplyr functions

filter, select, mutate, group by, summarise

```{r}
seatpos %>%
  filter(Age < 60 & Weight < 200) %>%
  select(Age, Weight) %>%
  mutate(decades = case_when(Age <=30 ~ "twenties",
                             Age <= 40 & Age >30 ~ "thirties",
                             Age <= 50 & Age >40 ~ "forties",
                             Age <= 60 & Age > 50 ~ "fifties")) %>%
  group_by(decades) %>%
  summarise(mean_Weight = mean(Weight))

         
```

### gather

gather columns into rows
```{r}
data("mtcars")
head(mtcars)
mtcars <- rownames_to_column(mtcars, "Model") %>%
  select(mpg, cyl, Model) %>%
  filter(cyl == 4)

gather(mtcars, "attribute", "this", 1:2)
```

### spread

spreads rows into columns

```{r}
data(mtcars)
mtcars <- rownames_to_column(mtcars, "Model") %>%
  select(mpg, cyl, Model)

spread(mtcars, key = 'cyl', value = 'mpg')

```

## linear modeling

linear models

### anova


```{r, eval=F}
### one way anova
library(faraway)
data(coagulation)
head(coagulation)

# boxplot
plot(coag ~ diet,coagulation,xlab="Diet",ylab="Coagulation Time")

# anova
anova(lm(coag ~ diet,coagulation))

# pairwise
tk_coag <- TukeyHSD(aov(coag ~ diet,coagulation))
tk_coag
plot(tk_coag)
```

### linear regression


``` {r}
# multiple regression
library(faraway)
data(savings)
head(savings)


## overall test
m1 <- lm(sr ~ pop15 + pop75 + dpi + ddpi,savings)
summary(m1)

# f stat for the overall test
ssy <- sum((savings$sr - mean(savings$sr))^2) # sum square y
sse <- deviance(m1) # residual sum of squares
df.residual(m1) # degress of freedom for the sse
fstat <- ((ssy-sse)/4)/(sse/df.residual(m1)) # F statistic for the overall test
1 - pf(fstat,4,df.residual(m1)) # p value

## partial f test

m2 <- lm(sr ~ pop75 + dpi + ddpi,savings) # reduced model
sse2 <- deviance(m2) # SSE for reduced model
fstat2 <- (deviance(m2)-deviance(m1))/(deviance(m1)/df.residual(m1))
1-pf(fstat2,1,df.residual(m1))


```
### interactions

``` {r}

library(faraway)
data(teengamb)

# income and sex on outcome
m1 <- lm(gamble ~ income + sex,teengamb)
#income, sex, and interaction between both
m2 <- lm(gamble ~ income + sex + income*sex,teengamb)

```

### correlation

``` {r}

library(faraway)
data(stat500)

m1 <- lm(final ~ midterm,stat500)
summary(m1)
sum(coef(m1)* c(1,83))
# confidence interval for beta 1
confint(m1)

# correlation

cor(stat500$final,stat500$midterm)

```
## functions and loops


### sample for loop
``` {r}
data(GSSvocab)
EGE<-rep(0,500)
for (i in 1:500)
{
  temp0<-na.omit(GSSvocab)
  index<-sample(1:27360,27360,replace=T) # random index
  temp1<-temp0[index,] # random sample of all data
  NewTrain<-temp1[1:13680,] # training data
  NewTest<-temp1[13681:27360,] # test data
  out<-lm(vocab~gender+nativeBorn+ageGroup+
             educGroup+age+educ,data=NewTrain)
  EGE[i]<-var(NewTest$vocab-predict.lm(out, newdata=NewTest))
}
summary(EGE)
hist(EGE,breaks = 20)
qqnorm(EGE)
quantile(EGE,probs=c(.025,.975))

```

### sample function
``` {r}
clean_live_frame_function <- function(livedata, albumname)  {
  artist_live_edits <- livedata %>%
    mutate(livemarker = ifelse(livedata$album_name == albumname, 1, 0))
  artist_live_edits2 <- artist_live_edits %>%
    mutate(omitvariable = case_when(
      (str_detect(album_name, "Sessions") |
         str_detect(album_name, "Live") |
         str_detect(album_name, "Festival") |
         str_detect(album_name, "Concerts"))& livemarker == 0 ~ "omit"))
 artist_live_edits2 <- artist_live_edits2 %>%
    mutate(omitvariable2 = case_when(
      (str_detect(track_name, "Live") & livemarker == 0 ~"omit")
    ))
 artist_live_edits2 <- artist_live_edits2 %>%
   filter(is.na(omitvariable) & is.na(omitvariable2))
 artist_live_edits2 <- artist_live_edits2 %>%
   distinct()
}

```

## numpy

### reticulate

``` {r setup2, include = TRUE}
#install.packages("reticulate")
library(reticulate)
use_python("/usr/bin/python")
#best way to install pandas may be to use this py_install function when in reticulate mode
py_install("pandas", pip = TRUE)
py_install("sklearn", pip = TRUE)
py_install("matplotlib", pip = TRUE)

```

### arrays

``` {python}
#basic array
array_1d = np.array([10, 11, 12, 13])
print (array_1d)
#array from a list
list_1 = [11, 22, 33, 44, 55]
array_l1 = np.array(list_1)
print(array_l1)
#create 1D array
array_1d = np.array([6,4,4,4,4,5,5,5,5])
print (array_1d)
#remember that python starts at 0
print('element at index1:', array_1d[0])

```



## pandas


### basic

``` {python}

#summarize mean values
df.groupby(['sepal width (cm)']).mean()

#duplicates
df.shape
df.drop_duplicates

#rename columns
df2 = df.rename({'petal width (cm)': 'Width of Petals'})
print(df2)

#check null values
df2.isnull()
df2.isnull().sum()

#drop missing values
df2.dropna(axis =1)
```

### more

``` {python}
#describe all values
df2.describe()

#count row totals
df2['Width of Petals'].value_counts().head(30)

#correlation
df2.corr()

#conditional selection
df2[df2['Width of Petals'] >= 2.3]

#complex conditional seection
df2[(df2['sepal length (cm)'] == 6.3) | (df2['sepal length (cm)'] == 6.4) ]

```




## scikit-learn


### train/test

``` {python}

#training and testing
X = df['sepal length (cm)'].values.reshape(-1,1)
y = df['sepal width (cm)'].values.reshape(-1,1)
X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=0.2, random_state=0)
regressor = LinearRegression()  
regressor.fit(X_train, y_train) #training the algorithm
#intercept
print(regressor.intercept_)
#slope
print(regressor.coef_)
```

### evaluation

``` {python}

#testing
y_pred = regressor.predict(X_test)
df = pd.DataFrame({'Actual': y_test.flatten(), 'Predicted': y_pred.flatten()})
df

#evaluation
print('Mean Absolute Error:', metrics.mean_absolute_error(y_test, y_pred))  
print('Mean Squared Error:', metrics.mean_squared_error(y_test, y_pred))  
print('Root Mean Squared Error:', np.sqrt(metrics.mean_squared_error(y_test, y_pred)))

### for multiple regression

X = df[['sepal width (cm)', 'sepal length (cm)']].values

```



## javascript D3.js

### r2d3 connection

r3d3 package with json data


``` {r echo=TRUE, eval = FALSE}

r2d3(data = jsonlite::read_json("data/my_weather_data.json"),d3_version = 4, script = "interaction.js")

```

### static bar

```{js echo=TRUE, eval = FALSE}
var svgWidth = 500, svgHeight = 500, barPadding = 10;
var barWidth = (svgWidth / 9);

var svg = d3.select('svg')
    .attr("width", svgWidth)
    .attr("height", svgHeight);
    
var yScale = d3.scaleLinear()
    .domain([0, d3.max(data)])
    .range([0, svgHeight]);
    
var xScale = d3.scaleLinear()
   .domain([0, 100])
   .range([0,width]);
        
var barChart = svg.selectAll("rect")
    .data(data)
    .enter()
    .append("rect")
    .attr("y", function(d) {
      return  svgHeight - d.liveness*900;
    })
    .attr("height", function(d) {
      return d.liveness*900;
    })
    .attr("width", barWidth - barPadding)
    .attr("transform", function (d, i) {
        var translate = [barWidth * i, 0]; 
        return "translate("+ translate +")";
    });

```
 
### dynamic

```{js echo=TRUE, eval = FALSE}
  
svg.selectAll("rect")
   .data(data)
   .enter()
   .append("rect")
   .attr("x", function(d,i){
     return i * (w/data.length);
   })
   .attr("y", function(d) {
     return h-(d.liveness*200);
   })
   .attr("width", w / data.length - barPadding)
   .attr("height", function(d) {
     return d.liveness * 200;
   })
   .attr("fill", "teal")
   .on("mouseover", function(d){
     d3.select(this)
     .attr("fill", "orange");
    })
   .on("mouseout", function(d){
     d3.select(this)
     .transition()
     .duration(750)
     .attr("fill", "teal");
    })
  .on("mouseover", function(d){
    var xPosition = parseFloat(d3.select(this).attr("x")) + xScale.bandwidth() / 2;
    var yPosition = parseFloat(d3.select(this).attr("y")) + 14;
  d3.select("#tooltip")
    .style("eft", xPosition + "px")
    .style("top", yPosition + "px")
    .select("#value")
    .text(d.tempo);
  d3.select("#tooltip").classed("hidden", false);
});

svg.selectAll("text")
  .data(data)
  .enter()
  .append("text")
  .text(function(d) {
    return d.track_name;
})
  .attr("x", function(d,i) {
    return i * (w/data.length);
  })
  .attr("y", function(d) {
    return h-(d.liveness*200) +15;
  })
  .attr("font-family", "sans-serif")
  .attr("font-size", "11px")
  .attr("fill", "white")
  .attr("text-anchor", "middle");
  
```

## external css

### css script

link with css: "style.css"


```{css echo=TRUE, eval = FALSE}

.body {
    display: flex;
    justify-content: center;
    padding: 5em 2em;
    font-family: sans-serif;
}

.tooltip {
    opacity: 0;
    position: absolute;
    top: -12px;
    left: 0;
    padding: 0.6em 1em;
    background: #fff;
    text-align: center;
    border: 1px solid #ddd;
    z-index: 10;
    transition: all 0.2s ease-out;
    pointer-events: none;
}
```

 
##  html

```{html echo=TRUE, eval = FALSE}
<html lang="en">
    <head>
        <link rel="stylesheet" href="./styles.css"></link>
        <title>Chart Title</title>
    </head>
    <body>
        <div id="wrapper" class="wrapper">
             <div class="tooltip-date">
                    <span id="date"></span>
      </div>
   </div>
</body>
</html>

```

 

