
---
title: ""
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


<style type="text/css">
.title {
  display: none;
}

#getting-started img {
  margin-right: 1px;
}

</style>

<div class="row" style="padding-top: 30px;">
<div class="col-sm-6">

# Overview



<a href = "https://wca.wharton.upenn.edu/students/analytics-fellows/" target = "_blank"> Wharton Analytics Fellows </a>is a fellowship program that unites graduate and undergraduate students across schools at Penn to consult with companies on analytics solutions for business practice. 



# YouTube clustering

2018 | 7 | 23 Last compiled: `r Sys.Date()`

Notice that whatever you define as a top level header, automatically gets put into the table of contents bar on the left. 

##### Second level header

You can add more headers by adding more hashtags. These won't be put into the table of contents


2018 | 7 | 23 Last compiled: `r Sys.Date()`

Sample Code

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```



# MLB Text Analysis

2018 | 7 | 23 Last compiled: `r Sys.Date()`

Notice that whatever you define as a top level header, automatically gets put into the table of contents bar on the left. 

##### Second level header

You can add more headers by adding more hashtags. These won't be put into the table of contents


2018 | 7 | 23 Last compiled: `r Sys.Date()`

Sample Code

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```





