
---
title: ""
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


<style type="text/css">
.title {
  display: none;
}

#getting-started img {
  margin-right: 1px;
}

</style>

<div class="row" style="padding-top: 30px;">
<div class="col-sm-6">

# Overview



<a href = "https://wca.wharton.upenn.edu/students/analytics-fellows/" target = "_blank"> Wharton Analytics Fellows </a>is a fellowship program that unites graduate and undergraduate students across schools at Penn to consult with companies on analytics solutions for business practice. 



# YouTube



Using a popular <a href = "https://www.kaggle.com/datasnaek/youtube-new/" target = "_blank"> Kaggle dataset </a> on trending videos from YouTube, I use an unsupervised learning algorithm to find trends on over 9,000 trending videos. Clustering results may inform sales team on pricing strategies for ads, or the product team to better understand content creation. 


### Technical

Data cleaning: tidyverse </br>
Clustering: factoextra

### Sample

Sample code and charts below. See <a href = "https://github.com/katjanewilson/YouTube" target = "_blank"> GitHub repo </a> for full code and analysis.

```{r echo=TRUE}
library(tidyverse)
load(file = "data/data1.Rdata")
df <- data %>%
  select(average_comments, average_dislikes,
         average_likes, average_views)

#scale the data
df<- scale(df)
library(factoextra)
distance <- get_dist(df)
plot<- fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))
plot

#to determine the optimal number of clusters
set.seed(123)

#function to compute total within-cluster sum of square 
wss <- function(k) {
  kmeans(df, k, nstart = 10 )$tot.withinss
}
k.values <- 1:15

# extract wss
wss_values <- map_dbl(k.values, wss)

plot(k.values, wss_values,
     type="b", pch = 19, frame = FALSE, 
     xlab="Number of clusters",
     ylab="Total Sum of Squares")

k2 <- kmeans(df[,(1:3)], centers = 3, nstart = 25)

df %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         names = row.names(data)) %>%
  ggplot(aes(average_views, average_comments, color = factor(cluster), label = names)) +
  geom_text(alpha = .7) +
  ggtitle("Clusters") +
  ylab("Average Comments" )+
  xlab("Average Views") +
  theme(legend.position = "none") +
  theme_minimal()
```




# MLB


Using psychometric and performance data from an MLB team, we analyzed how a player's psych data influences their performance statistics at the major league level.


### Technical

Data cleaning: tidyverse
Text Mining: tm package, tidytext
Clustering: hclust, PCA

### Sample
